`flippant` -- An `R` package for the automated  analysis of dithionite

### 2015-09-17 inst/manuscript/manuscript.rmd
Ensure code highlighting of function calls (knitr author);

library(mvbutils)
```

@@

#Input Data and Data Processing
To analyse raw data stemming from dithionite scramblase assays, `flippant` 
requires for each data point information as the path to the 
fluorometer-generated spectrum, the amount of protein used to reconstitute 
proteoliposomes, the volume used in the assay before and after addition of 
dithionite (to calculate a volume correction factor), the amount of lips 
present (to calculate a proteine to phospholipid ratio or PPR) etc. The 
following function generates a spreadsheet program-compatible tab-delimited 
#Main Features
##Template Generation for Data Input
The following function generates a spreadsheet program-compatible tab-delimited 
`ASCII` template including column names, commentary, expected data type and the 
default used when ommited, supporting the user in providing the data needed in 
one table row per data point.
```{r echo = FALSE, comment = ""}
make.usage.section("scramblaseAssayInputTemplate", env = asNamespace("flippant"))
```
The application agnostic tab-delimited format must be maintained for the 
completed table, which is subjected to extensive input checks when read by 
`flippant`.

@@

##Graphic Representation of Spectral Traces
```{r echo = FALSE, comment = ""}
make.usage.section("scramblaseAssayTraces", env = asNamespace("flippant"))
```

##Producing Protein To Phospholipid (PPR) Plots
```{r echo = FALSE, comment = ""}
make.usage.section("scramblaseAssayPlot", env = asNamespace("flippant"))
```

##Non-graphical Output of Analysis Results
```{r echo = FALSE, comment = ""}
make.usage.section("scramblaseAssayStats", env = asNamespace("flippant"))
```

>>>>

```

@@

#Input Data and Data Processing
To analyse raw data stemming from dithionite scramblase assays, `flippant` 
requires for each data point information as the path to the 
fluorometer-generated spectrum, the amount of protein used to reconstitute 
proteoliposomes, the volume used in the assay before and after addition of 
dithionite (to calculate a volume correction factor), the amount of lips 
present (to calculate a proteine to phospholipid ratio or PPR) etc. The 
following function generates a spreadsheet program-compatible tab-delimited 
#Main Features
##Template Generation for Data Input
The following function generates a spreadsheet program-compatible tab-delimited 
`ASCII` template including column names, commentary, expected data type and the 
default used when ommited, supporting the user in providing the data needed.
```{r, code=formatR::usage('scramblaseAssayInputTemplate'), eval=FALSE}
```
The application agnostic tab-delimited format must be maintained for the 
completed table, which is subjected to extensive input checks when read by 
`flippant`.

@@

##Graphic Representation of Spectral Traces
```{r, code = formatR::usage('scramblaseAssayTraces'), eval = FALSE}
```

##Producing Protein To Phospholipid (PPR) Plots
```{r, code = formatR::usage('scramblaseAssayPlot'), eval = FALSE}
```

##Non-graphical Output of Analysis Results
```{r, code = formatR::usage('scramblaseAssayStats'), eval = FALSE}
```
